Final Presentation

### 2023-04-18 Final Presentation.Rmd

## Primary Dataset: Citations in HTX
Insert description

@@

## Exploration
- bullet 
- point

>>>>

## Primary Dataset: Citations in HTX
- Citation Data in Houston, obtained from Stanford Open Policing Project
- Consists of collection of over 2,000,000 stops over various variables

@@

## Exploration
- Understand and contextualize primary dataset
- Investigate trends that may exhibit potential bias
- Examined distribution of citations over time, distribution by demographic and distribution by location
